An Empirical Analysis of the Role of Energy in Economic Growth

### 2013-07-07 EconGrowth.Rnw
Cleaned up several to-do items.

\section*{To-do List}
\begin{itemize}
\item{Pruim: At present, we are doing simple ± t-value * std. dev. for
      confidence intervals of, e.g., $1-\alpha-\beta$ in some places. 
      Is that still correct if we move to a different approach for 
      estimating confidence intervals? See especially \texttt{cesData} 
      and possibly other places.}
\item{Pruim: At present, we are doing \texttt{deltaMethod} for determining CIs on 
      $1-\alpha-\beta$ terms. Is that OK if we move to a different approach
      for estimating confidence intervals?}
\item{Heun: Fix error when calculating confidence intervals for 
Cobb-Douglas model for TZ with X. The problem occurs in function 
\texttt{cobbDouglasData}. To repeat the problem, call \\* 
\texttt{cobbDouglasData(countryAbbrev="TZ", energyType="X")}. \\* 
The code fails on the line \\* 
\texttt{  ciCD <- confint(object=modelCD, level=ciLevel)}. \\* 
There is code after the to-do list in this file that exposes the problem.}
\item{Heun: Get function \texttt{cdModel} working with constraints. 
Note that the unconstrained solutions are sometimes within the constraints. 
But, sometimes they aren't. All solutions need to be within constraints. 
We may need to run with warnings turned off to view the problems.}
\item{Heun: Get function \texttt{cdeModel} working with constraints. 
Note that the unconstrained solutions are sometimes within the constraints. 
But, sometimes they aren't. All solutions need to be within constraints. 
We may need to run with warnings turned off to view the problems.}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Get values and se for $\sigma$s directly from the 
            \texttt{cesModel} object in the \texttt{cesData} function}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Eliminate blanks in the coefficient tables for the 
      95\% CIs in the Cobb-Douglas with energy rows}
      \begin{itemize}
      \item{ZA: lower bound on $\lambda$ and upper bound on $\alpha$}
      \item{ZM: lower bound on $\lambda$}
      \end{itemize}
\item{Heun: Eliminate blanks in the coefficient tables for the 95\% CIs in the LINEX model}
      \begin{itemize}
      \item{ZM: upper bound on $c_t$}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\item{\st{Heun: Get Pruim set up on the GitHub repository.}}
\end{itemize}

>>>>

\section*{To-do List}
\begin{itemize}
\item{Heun: Figure out why CESe for ZA with X fails during resampling.}
\item{Heun: Review all assumptions for CES with energy models. 
There are several assumptions for rho and rho1 for various countries. 
When we are resampling, we probably don't want to specify those values.}
\item{Heun: Implement confidence interval calculations for 
all resampling methods.}
\item{Heun: Decide if the single factor models should include constraints
on $\alpha$, $\beta$, and $\gamma$. At present, the single-factor model allows
values outside the ranges $\alpha \in (0,1)$, $\beta \in (0,1)$, and $\gamma \in (0,1)$.}
\item{Heun: Make smaller cloud plots for resample coefficients for those 
countries where $u$ is involved.}
\item{Heun: Investigate possible conflicting use of exergy by Warr and Ayres.}
\item{Heun: Get AIC calculations working again.}
\item{Heun: Fix the energy sankey diagram from the seminar}
\item{Heun: Include adjusted sankey diagram in the seminar}
\item{Heun: Add CES production function fits}
      \begin{itemize}
      \item{Write up the decisions about parameter estimation for the 
            CES production function fits}
      \item{Revisit my assumptions for the CES production function 
            (with energy) for each country.}
      \item{Fix the problems with $\sigma_1$ and $\sigma$ values in 
            the CES parameter tables in the appendix}
      \item{Add CES rows to the AIC table. Code is in the 
            \texttt{createAICTable} function, but it is not yet working. 
            Need to find a way to calculate AIC for the object that is 
            returned from the \texttt{cesEst} function.}
      \end{itemize}
\item{Heun: Fix warnings of the form \texttt{Warning:  step factor 0.000488281 reduced below ’minFactor’ of 0.000976562} in the code that generates the Cobb-Douglas with energy fits.}
\item{de Wit: review, critique, and contextualize.}
\end{itemize}
